Andres Karjus

### 2018-06-05 index.Rmd
fixes to redesign

<IMG SRC="IMG_2657.jpg" ALIGN="right" BR CLEAR="left" style="margin-left:10px; width: 60%; height: auto;"; /> 
<div style="text-align: justify"> 
I am a PhD student in linguistics based at the [Centre for Language Evolution at the University of Edinburgh](http://www.lel.ed.ac.uk/cle/), working on lexical dynamics and evolutionary variant selection in language with [Kenny Smith](http://www.lel.ed.ac.uk/~kenny), [Simon Kirby](http://www.lel.ed.ac.uk/~simon) and [Richard A. Blythe](http://www2.ph.ed.ac.uk/~rblythe3/), utilizing massive corpora and natural language processing to hunt traces of selection and competition between elements of language. My research is supported by a Kristjan Jaak scholarship from the Archimedes Foundation of Estonia. I am also affiliated with the University of Tartu as a (part-time) junior researcher in sociolinguistics at the [EKKAM](http://ekkam.ut.ee/en/) research group, specializing in data analysis and agent-based models. Besides research, I am also engaged in [teaching and consulting](https://andreskarjus.github.io/#teaching,_consulting_&_R workshops) data sciency things for the humanities.

@@

@@

Feel free to get in touch if you are interested in inviting me to teach a workshop on anything related to data science and statistics for the humanties, data visualization, R, corpus linguistics, natural language processing, digital humanities, etc.
</div>

@@

Besides research and teaching and consulting and whatnot, I (fortunately) also do other things, which currently mostly consist of dance (lindy hop, salsa, bachata), listening to jazz, outdoorsy stuff (cycling, hillwalking and scrambling), boardgames, and various other things. I also blog about the wonderful oddities of life abroad (but it's all in [untranslatable Estonian](http://postkaartkaledooniast.blogspot.com)). In earlier years, I worked various studenty sort of jobs to support my studies (not to list them all, but one of them involved swords and another one regularly mowing grass off the roof of a building).

@@

Before coming to Edinburgh, I worked as a teaching assistant in informatics at the University of Tartu, before that studied artificial intelligence and natural language processing at KU Leuven (MSc) and linguistics at the University of Tartu (BA, MA). Somewhere in between I also did exchanges to the University of Iceland and the University Vienna, attended a dozen-odd academic summer schools, taught Icelandic to art students and Estonian to Norwegian teachers, worked as an assistant at the Estonian Wordnet project, and did internships at CrossLang NV in Belgium and at the (then still existing linguistics department of the) Max Planck Institute for Evolutionary Anthropology in Leipzig.
</div>

## Contact

<a href="mailto:a.karjus--at--sms.ed.ac.uk"> @ </a> | <a href="https://twitter.com/AndresKarjus?ref_src=twsrc%5Etfw" class="twitter-follow-button" data-size="large" data-show-screen-name="false" data-show-count="false">@AndresKarjus</a><script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

<br>

>>>>

<IMG SRC="IMG_2657.jpg" ALIGN="right" BR CLEAR="left" style="margin-left:10px; width: 50%; height: auto;"; /> 
<div style="text-align: justify"> 
I am a PhD student in linguistics based at the [Centre for Language Evolution at the University of Edinburgh](http://www.lel.ed.ac.uk/cle/), working on lexical dynamics and evolutionary variant selection in language with [Kenny Smith](http://www.lel.ed.ac.uk/~kenny), [Simon Kirby](http://www.lel.ed.ac.uk/~simon) and [Richard A. Blythe](http://www2.ph.ed.ac.uk/~rblythe3/), utilizing massive corpora and natural language processing to hunt traces of selection and competition in language. This research is supported by a Kristjan Jaak scholarship from the Archimedes Foundation of Estonia. I am also affiliated as a (part-time) junior researcher with the University of Tartu [EKKAM](http://ekkam.ut.ee/en/) sociolinguistics group, working on data visualization and agent-based models. I am also engaged in [teaching and consulting](https://andreskarjus.github.io/#teaching,_consulting_&_R workshops) data sciency things for the humanities. On the right is the picture obligatory for all academic home pages to subtly suggest that in fact I do not spend _all_ my time in the office at all.

@@

<br>
<br>

@@

Feel free to get in touch if you are interested in inviting me to teach a workshop on anything related to data science and statistics for the humanties, data visualization, R, corpus linguistics, natural language processing, digital humanities, etc.
</div>
<br>

@@

Besides research and teaching and consulting and whatnot, I (fortunately) also do other things, which currently mostly consist of dance (lindy hop, salsa, bachata), listening to jazz, outdoorsy stuff (cycling, hillwalking and scrambling), boardgames, and various other things. I also blog about the wonderful oddities of life abroad (but it's all in [untranslatable](http://postkaartkaledooniast.blogspot.com) Estonian).

@@

Before coming to Edinburgh, I worked as a teaching assistant in informatics at the University of Tartu, before that studied artificial intelligence and natural language processing at KU Leuven (MSc) and linguistics at the University of Tartu (BA, MA). Somewhere in between I also did exchanges to the University of Iceland and the University Vienna, attended a dozen-odd academic summer schools, taught Icelandic to art students and Estonian to Norwegian teachers, worked as an assistant at the Estonian Wordnet project, and did internships at CrossLang NV in Belgium and at the (then still existing linguistics department of the) Max Planck Institute for Evolutionary Anthropology in Leipzig. In earlier years, I worked various studenty sort of jobs to support my studies (not to list them all, but one of them involved swords and another one regularly mowing grass off the roof of a small yellow building).
</div>
<br>

## Contact
<br>
<br>
<div style="text-align: center"> 
<a href="mailto:a.karjus--at--sms.ed.ac.uk">email</a>  |  <a href="https://twitter.com/AndresKarjus">twitter</a>
<br>
</div>
